### 2022-08-26 paper/sections/results.tex
Begin writing a bit on HMC
- update some figures using the new analysis methods

\begin{figure*}
    \includegraphics[width=0.7\textwidth]{graham_density_prior_pred_log10_Sigma_mean.png}
    \caption{\drafting{Prior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid. From the prior predictive estimate, it is seen that the model and the assumed parameter hyperdistributions are able to describe the observed data, in that the observed data lies within the range allowed by the prior predictive estimate. TODO?? This isn't a true prior predictive test, as the independent variable $R$ is not the $R$ of the data but some arbitrary range. Change it?}}
    \label{fig:priorpred}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{graham_density_pair_0.png}
    \caption{\drafting{Corner plot of hierarchical model hyperparameters. Each of the hyperdistributions are modelled as Gamma distributions with shape parameters $\alpha$ and $\beta$. For example, the hyperdistribution on the core radius $r_\mathrm{b}$ is modelled as $r_\mathrm{b} \sim \text{Gamma}(r_{\mathrm{b},\alpha}, r_{\mathrm{b},\beta})$. Critically, the hyperdistributions are unimodal with highest-density regions located some distance from the distribution edges, indicating the HMC sampling has converged well. }}
    \label{fig:corner_params_1}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{graham_density_pair_1.png}
    \caption{\drafting{Same as \ref{fig:corner_params_1}}}
    \label{fig:corner_params_2}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{graham_density_posterior_pred_log10_Sigma_mean.png}
    \caption{\drafting{Posterior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid, and seen to lie well within the 50\% BCI. }}
    \label{fig:postpred}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\textwidth]{{graham_density-A-C-3.0-0.05_prior_pred_log10_proj_density_mean}.png}
    \caption{\drafting{Prior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid. From the prior predictive estimate, it is seen that the model and the assumed parameter hyperdistributions are able to describe the observed data, in that the observed data lies within the range allowed by the prior predictive estimate.}}
    \label{fig:priorpred}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_pair_0}.png}
    \caption{\drafting{Corner plot of hierarchical model hyperparameters. Each of the hyperdistributions are modelled as Gamma distributions with shape parameters $\alpha$ and $\beta$. For example, the hyperdistribution on the core radius $r_\mathrm{b}$ is modelled as $r_\mathrm{b} \sim \text{Gamma}(r_{\mathrm{b},\alpha}, r_{\mathrm{b},\beta})$. Critically, the hyperdistributions are unimodal with highest-density regions located some distance from the distribution edges, indicating the HMC sampling has converged well. }}
    \label{fig:corner_params_1}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_pair_1}.png}
    \caption{\drafting{Same as \ref{fig:corner_params_1}}}
    \label{fig:corner_params_2}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_posterior_pred_log10_proj_density_mean}.png}
    \caption{\drafting{Posterior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid, and seen to lie well within the 50\% BCI. }}
    \label{fig:postpred}
\end{figure*}
